---
title: "Sharafi_HW6"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
```

## Question 1
First read the Data
```{r, include=FALSE}
pn <- read_csv("~/Desktop/ES207/HW/es207_hw3/data/eesR/R/Data/pollution.csv", col_names = TRUE, na = c("NA", "n/p", "n/a"), guess_max = 30000)

```
Draw scatter plot of **mortality rat** versus level of **nitric oxides**
```{r}
p <- ggplot(pn, aes(x =nox, y = mort)) + 
  theme_bw() +geom_point(alpha = 0.5) +
  geom_smooth(method = "lm") + ylim(c(600,1100))
p
```
Create the regression model 
```{r}
lm1 <- lm(mort ~ nox, data = pn)
summary(lm1)
```
Since the R-squared in **negative**, The mean of the data provides a better fit to the outcomes than do the fitted function values.Then fit the regression with ressidual in to the plot 
```{r}
pn$predicted <- predict(lm1)
pn$residuals <- residuals(lm1)
pn %>% 
  ggplot(aes(x = nox, y = mort)) +
  theme_bw()+
  geom_segment(aes(xend = nox, yend = predicted), alpha = .75) +
  geom_point(aes(color = residuals)) +
  scale_color_gradient2(low = "blue", mid = "white", high = "red") +
  guides(color = FALSE) +
  geom_point(aes(y = predicted), shape = 1)
```

Definitely need transformation 
## Question 2
In **4b** we use 'ln' for transformation, and tranformed 'nox'
```{r}
 ggplot(pn, aes(x = log(nox), y = mort )) + 
  theme_bw() +geom_point(alpha = 0.5) +
  geom_smooth(method = "lm") + ylim(c(700,1200))
```

And ressidual plot.
```{r}
lm2 <- lm(mort ~ log(nox), data = pn)
pn$predicted <- predict(lm2)
pn$residuals <- residuals(lm2)
pn %>% 
  ggplot(aes(x = log(nox), y = mort  )) +
  theme_bw()+
  geom_segment(aes(xend = log(nox), yend = predicted), alpha = .75) +
  geom_point(aes(color = residuals)) +
  scale_color_gradient2(low = "blue", mid = "white", high = "red") +
  guides(color = FALSE) +
  geom_point(aes(y = predicted), shape = 1)
```

In **4c** find the slope with summary 
```{r}
lm2 <- lm(mort ~ log(nox), data = pn)
summary(lm2)
```
The slope is  15.335 ,the change in **mortality rat** for a unit change in **nitric oxides**.Which represents the change in the response variable,mort  per unit change in the predictor here nox .  

## Question 5
4d in Qian. 
```{r}
# Model predicting mortality rate using levels of:
# HC     Relative hydrocarbon pollution potential
# NOX    Same for nitric oxides
# SO2    Same for sulphur dioxide

lm4d <- lm(mort~nox + hc + so2, data = pn)
summary(lm4d)
```


```{r}

```


